---
title: Retrospectively sweaty? The effects of temperature changes on presidential approval
subtitle: POL837 Issues in Comparative Politics Research Paper
format: clean-revealjs
author:
  - name: Daniel Sánchez Pazmiño
    affiliations: Simon Fraser University
date: "2024-04-01"
date-format: "MMMM YYYY"
bibliography: references.bib
csl: apa7_normal.csl
knitr: 
  opts_chunk: 
      echo : false
      message: false
      warning: false
---

```{r setup}
#| label: setupq
#| include: false
library(ggdag, warn.conflicts = F)
```

# Introduction

- Ideally, voters can adequately assess the performance of elected officials to hold them accountable at the ballot box.

- However, evaluations of political performance can be influenced by factors unrelated to politican performance [@healyIrrelevanteventsaffect2010; @healyRandomeventseconomic2010; @achenBlindretrospectionelectoral2017]

- I investigate whether transient temperature changes affect retrospective evaluations of  presidential performance in Ecuador, using CPC weather data and the AmericasBarometer public opinion survey. 

- Results show that a 1°C increase in maximum temperature leads to a **1.9 - 2.2 p.p.** decrease in the likelihood of presidential approval. 

::: {.notes}
- The literature suggests that efficient systems of retrospective voting can lead to greater democratic accountability and efficient political outcomes [@besleyPrincipledagentspolitical2006; @perssonPoliticaleconomicsexplaining2002]

- Factors include cognitive bias, recency bias, heuristics, party cues, among others. 

- Shark attacks, draughts, football matches, among others. 
:::

# Theoretical framework

- I hypothesize that temperature affects presidential approval through mood.

```{r}
#| label: dag

dag <- dagify(
  presidential_approval ~ temperature,
  temperature ~ mood
)

ggdag(dag) + 
  theme_dag()
```

# Empirical strategy

# Results

# Conclusion